Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-06-22 doc/ms.tex
Update velocity figs, and provide uncertainties on the best-fit time of explosion.

We fit the measured velocities of \ion{Si}{2}\,$\lambda$6355 to the
$v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value
and find the best-fit explosion time $t_{exp} = -17.95\,\textrm{days}$
with a 3-$\sigma$ confidence interval between $-17.4\,\textrm{days}$
and $-18.3\,\textrm{days}$ (Figure \ref{fig:velocity_t_exp}). We additionally
alter the power-law index to $-0.20$ and $-0.24$ to examine the
sensitively of the result on the assumed power-law index.  This 
leads to consistent results within the respective 3-$\sigma$ 
confidence intervals. \amiller{This analysis needs to be updated to reflect the new time of maximum}

Comparing our estimates for $t_{exp}$ and $t_0$ (left panel of 
Figure \ref{fig:velocity_t_exp}), we find that 
$t_0\lessapprox t_{exp}$.\footnote{Note that the uncertainties on $t_{exp}$ are large due to assumptions in the $v\propto(t-t_{exp})^{-0.22}$ model.}
Since physical causality requires $t_{exp}<t_0$, we draw the qualitative
conclusion that $t_0\simeq t_{exp}$, which is consistent
with our inference from the early light curve analysis (Section
\ref{sec:lc_fit}).

>>>>

We fit the measured velocities of \ion{Si}{2}\,$\lambda$6355 to the
$v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_{exp} = -17.45 \pm ^{0.14}_{0.16}\;\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}). Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitively of the result on the assumed power-law index. We find that this variation in the power-law index result in inferred explosion times that vary by $\approx$1 d (Figure \ref{fig:velocity_t_exp}). Given the theorhetical expectation that $v \propto t^{-0.22}$, we adopt $t_{exp} = -17.45 \pm 0.5 \; \mathrm{d}$, where the uncertainty reflects possible variations in the power-lax index (see \citealt{2014ApJ...784...85P}).

Comparing our estimates for $t_{exp}$ and $t_0$ (left panel of 
Figure \ref{fig:velocity_t_exp}), we find that 
$t_0\lessapprox t_{exp}$.
Since physical causality requires $t_{exp}<t_0$, we draw the qualitative
conclusion that $t_0\simeq t_{exp}$, which is consistent to within the uncertainties.
